\documentclass[]{article}
\usepackage{lmodern}

\usepackage{xcolor}

\usepackage{sectsty}

\sectionfont{\sffamily\Huge\centerline}
\subsectionfont{\sffamily\Large\underline}

\setlength{\parskip}{0pt plus 2pt minus 0pt}

\usepackage{enumitem}
\setlist[itemize]{topsep=3pt,leftmargin=20pt}
%% \setlist[itemize,1]{label=$\ovoid$}

\definecolor{maroon}{HTML}{992626}

\newcommand{\localtextbulletone}{\textcolor{maroon}{\raisebox{.45ex}{\rule{.6ex}{.6ex}}}}
\renewcommand{\labelitemii}{\localtextbulletone}
\renewcommand{\labelitemi}{\localtextbulletone}



\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
    \setmainfont{Adobe Caslon Pro}
    \setsansfont{Myriad Pro}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=0.75in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt plus 3pt minus 0.5pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\date{}

\begin{document}

\section{James J Porter}\label{james-j-porter}

web: \emph{jamesporter.me}

mail: \emph{james@jamesporter.me}

\subsection{Education}\label{education}

\begin{itemize}
\item
  \textbf{The University of Chicago} --- Chicago, Illinois

  \emph{Biological Sciences, Minor in Computer Science}, 2014

  GPA 3.98/4.0
\item
  \textbf{Chardon High School} --- Chardon, Ohio

  2010

  GPA 4.0/4.0
\end{itemize}

\subsection{Experience}\label{experience}

\begin{itemize}
\item
  \textbf{Software Developer}, 2013-2014

  \emph{Center for Data Intensive Science} --- Chicago, Illinois

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Developed, deployed, and improved software infrastructure for doing
    bioinformatic analyses on cloud computing systems, primarily using
    Python.
  \end{itemize}
\item
  \textbf{Core Tutor}, 2013-2014

  \emph{University of Chicago Department of Computer Science} ---
  Chicago, Illinois

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Tutored introductory computer science students in Racket, Java,
    Haskell, and Python.
  \end{itemize}
\item
  \textbf{Hacker School}, 2013

  New York City, NY

  hackerschool.com

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    ``a writer's retreat for programmers.''
  \item
    Studied new programming languages, fields, techniques, etc.
  \item
    Contributed to a variety of open source projects.
  \end{itemize}
\item
  \textbf{Laboratory Teaching Assistant}, 2012-2013

  \emph{University of Chicago Biological Sciences Division} --- Chicago,
  Illinois

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Instructed first-year students in experimental and computational
    molecular biology lab techniques.
  \item
    Managed a teaching laboratory of 14-20 students for four hours each
    week.
  \item
    Taught scientific programming with Matlab, taking students from zero
    knowledge to implementing models of genetic switches.
  \end{itemize}
\item
  \textbf{Undergraduate Research}, 2011-2013

  \emph{Ilaria Rebay Lab}, University of Chicago Ben May Department for
  Cancer Research --- Chicago, Illinois

  \begin{itemize}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    Designed, implemented, and optimized simulations of genetic systems.
  \item
    Performed experiments aimed at understanding mechanisms of
    transcriptional repression in fruit flies.
  \item
    Facilitated collaboration between three research groups at two
    universities.
  \end{itemize}
\end{itemize}

\subsection{Skills}\label{skills}

\subsubsection{Computational}\label{computational}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Experience using and programming UNIX systems and associated tools.
\item
  Competent user of (in approximate order of familiarity) Python, C,
  Julia, Javascript, Lisp(s), shell scripting, Git, HTML/CSS, Matlab,
  Mathematica, various others.
\item
  Comfortable programing in a wide variety of domains and styles.
\end{itemize}

\subsubsection{Laboratory}\label{laboratory}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Molecular biology (cloning, PCR, etc.)
\item
  Microinjections
\item
  Confocal fluorescence microscopy
\item
  Care and breeding of \emph{Drosophila melanogaster}
\end{itemize}

\subsection{Honors and Awards}\label{honors-and-awards}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Phi Beta Kappa Society, 2013
\item
  Barry M. Goldwater Scholarship, 2013
\item
  BSCD Fellowship, \emph{University of Chicago Biological Sciences
  Division}, 2012
\item
  Research Experiences for Undergraduates Fellowship, \emph{Chicago
  Center for Systems Biology}, 2011
\item
  National Merit Scholarship Finalist, 2010
\item
  National AP Scholar, 2010
\item
  Robert Byrd Scholarship, 2010
\item
  Eagle Scout, \emph{Boy Scouts of America, Troop 93}, 2009
\end{itemize}

\end{document}
